---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidscreen

<!-- badges: start -->
[![CI-CD](https://github.com/jesse-smith/covidscreen/workflows/CI-CD/badge.svg)](https://github.com/jesse-smith/covidscreen/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/covidscreen)](https://CRAN.R-project.org/package=covidscreen)
<!-- badges: end -->

{covidscreen} is an R package and Shiny app designed to help organizations evaluate their risk from COVID-19 and the potential benefits of regular asymptomatic testing.

## Installation

You can install the development version of {covidscreen} from Github with:

``` r
if (!"remotes" %in% installed.packages()) install.packages("remotes")
remotes::install_github("jesse-smith/covidscreen")
```

If you are using R on Windows, you will need to first install Rtools [here](https://cran.r-project.org/bin/windows/Rtools/).

## Example

```{r library}
library(covidscreen)
```

To run the Shiny app, you can use `run_app()` or visit an [online version](https://jesse-shiny.shinyapps.io/covidscreen/).

To access the underlying model in **R**, you can use `cs_dist()` with the desired parameters. Running with no inputs uses the defaults; the output is a `data.table`:

```{r cs_dist}
# Create some data using default parameters
data <- cs_dist()

# Show data
data
```

You can access the risk-based metrics used in the Shiny app using corresponding
functions in the R package. Undetected cases are calculated using
`cs_undetected()`, relative risk reduction is calculated using `cs_rr()`, and
cost effectiveness per test is calculated using `cs_cost_eff()`.

```{r risk-metrics}
# Cost effectiveness
cs_undetected(data)

# Relative risk reduction
cs_rr(data)

# Cost effectiveness
cs_cost_eff(data)
```

Additionally, test performance metrics are included in the R package to
facilitate analysis not performed in the Shiny app. These include:

* `cs_pos()`: the proportion of positive tests (out of the organization)
* `cs_neg()`: the proportion of negative tests (out of the organization)
* `cs_true_pos()`: the proportion of true positive tests (out of org)
* `cs_true_neg()`: the proportion of true negative tests (out of org)
* `cs_false_pos()`: the proportion of false positive tests (out of org)
* `cs_false_neg()`: the proportion of false negative tests (out of org)
* `cs_ppv()`: the positive predictive value of a test
* `cs_npv()`: the negative predictive value of a test
* `cs_fdr()`: the false discovery rate of a test
* `cs_for()`: the false omission rate of a test
* `cs_sens()`: the sensitivity (true positive rate, recall) of a test
* `cs_spec()`: the specificity (true negative rate) of a test
* `cs_fpr()`: the false positive rate of a test
* `cs_fnr()`: the false negative rate of a test

```{r test-metrics}
# Positive tests
cs_pos(data)

# Negative tests
cs_neg(data)

# True positives
cs_true_pos(data)

# True negatives
cs_true_neg(data)

# False positives
cs_false_pos(data)

# False negatives
cs_false_neg(data)

# Positive predictive value (precision)
cs_ppv(data)

# Negative predictive value
cs_npv(data)

# False discovery rate
cs_fdr(data)

# False omission rate
cs_for(data)

# True positive rate (sensitivity/recall)
cs_sens(data)

# True negative rate (specificity)
cs_spec(data)

# False positive rate
cs_fpr(data)

# False negative rate
cs_fnr(data)
```

## Code of Conduct

Please note that the {covidscreen} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
