---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidtest

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/jesse-smith/covidtest/workflows/CI-CD/badge.svg)](https://github.com/jesse-smith/covidtest/actions)
[![Codecov test coverage](https://codecov.io/gh/jesse-smith/covidtest/branch/master/graph/badge.svg)](https://codecov.io/gh/jesse-smith/covidtest?branch=master)
<!-- badges: end -->

{covidtest} is an R package and Shiny app designed to help organizations evaluate their risk from COVID-19 and the potential benefits of regular asymptomatic testing.

## Installation

You can install the development version of {covidtest} from Github with:

``` r
if (!"remotes" %in% installed.packages()) install.packages("remotes")
remotes::install_github("jesse-smith/covidtest")
```

If you are using R on Windows, you will need to first install Rtools [here](https://cran.r-project.org/bin/windows/Rtools/).

## Example

```{r library}
library(covidtest)
```

To run the Shiny app, you can use `run_app()` or visit an [online version](https://jesse-shiny.shinyapps.io/covidtest/).

To access the underlying model in **R**, you can use `ct_dist()` with the desired parameters. Running with no inputs uses the defaults; the output is a `data.table`:

```{r ct_dist, eval=FALSE, include=FALSE}
ct_dist()
```

## Code of Conduct

Please note that the {covidtest} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
